Chapter 3 practice problems

### 2023-09-14 Stats Rethinking/Ch3/Dr_Parson_ch_3_problems.Rmd
Notes through 4.3.4

#3e4
```{r}
quantile(samples, 0.2)
```

#3e5
```{r}
quantile(samples, 0.8)
```

@@

ggplot() +
  geom_line(mapping = aes(x = grid, y = posterior * N))
```
I scaled the probabilities in the posterior by N for the graph to match the vertical scale of the density below.

@@

```
```{r}
grid[which.max(posterior)]
```

@@

```{r}
ggplot() +
  geom_density(mapping = aes(x = simulated))
```
#3h4

@@

```{r}
births %>% filter(birth1 == 0, birth2 == 1) %>% count()
```
```{r}
births %>% filter(birth1 == 0) %>% count()
```
```{r}
simulate_girl_first <- rbinom(n = 1e4, size = 49, prob = samples)
```

>>>>

#3e4

```{r}
quantile(samples, 0.2)
```

#3e5

```{r}
quantile(samples, 0.8)
```

@@

I scaled the probabilities in the posterior by N for the graph to match the vertical scale of the density below.

@@

```

```{r}
grid[which.max(posterior)]
```

@@

```{r}
ggplot() +
  geom_density(mapping = aes(x = simulated))
```

#3h4

@@

```{r}
births %>% filter(birth1 == 0, birth2 == 1) %>% count()
```

```{r}
births %>% filter(birth1 == 0) %>% count()
```

```{r}
simulate_girl_first <- rbinom(n = 1e4, size = 49, prob = samples)
```
